---
title: "R Notebook"
output: html_notebook
---

```{r}
load("hw2_list.rda")
```

```{r}

```

### create a nested List from df_names as levels/parent and numeric vars and sumstats
```{r}

attributes(bp_list)
typeof(bp_list)
str(bp_list)

get_df_names <- function(bp_list, stat = "mean"){
    stat__ <- get(stat)
    df_names <- list()
    for(item in names(bp_list)){
        df_names <- append(df_names, item)
        numeric_var_names <- list()
        df_stats <- list()
        for (j in bp_list){
            numeric_var_names <- append(numeric_var_names,(names(j)[sapply(j,is.numeric)]))
            df_stats <- append(df_stats, list(stat__(j$pre_bp), stat__(j$post_bp), stat__(j$diff_bp)))
        }
    } 
    return(list(df_names, numeric_var_names, df_stats))
}
dfnamestst <- get_df_names(bp_list)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

